---
title: "Naming Ham-let/National Hurling League 2020"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Rules

There are 3 division: 1A, 1B, 2A

1. Winner of each division will enter the top 3
1. Winner out of the top 3 will be determined highest points scored by an individual player in the team through the entire season (including knockout games)
1. If highest individual points is a tie, the tie is broken by most number of “three-pointers” (aka “goals” by us hurling enthusiasts)
1. If still tied then Baby Mama gets to pick

## Division 1A

```{r scrape}

source(here::here("scripts/tables.R"))

knitr::kable(babyname_points %>% filter(division == "1A"))

```

## Division 1B

```{r}
knitr::kable(babyname_points %>% filter(division == "1B"))
```

## Division 2A

```{r}
knitr::kable(babyname_points %>% filter(division == "2A"))
```


